Tidal streams in triaxial systems

### 2015-04-14 ms.tex
add authors

% packages
\usepackage{amssymb,amsmath,amsbsy}
\usepackage{bbold}
\usepackage{arydshln}
\usepackage{algpseudocode}
\renewcommand\algorithmicthen{}
\renewcommand\algorithmicdo{}
\usepackage{mathrsfs}
\usepackage{subfigure}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}

@@

\title{Tidal streams in triaxial systems}
\author{Adrian M. Price-Whelan\altaffilmark{\colum,\adrn},
	    Kathryn V. Johnston\altaffilmark{\colum},
	    Monica Valluri\altaffilmark{\mich}}
\date{\centering \today}

@@

\acknowledgements
The authors wish to thank Sarah Pearson, Robyn Sanderson, Andreas K\"upper, David Hogg, Dan D'Orazio, David Merritt, and the \emph{Stream Team} for useful comments and discussion.
APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155. 
This research made use of Astropy, a community-developed core \texttt{Python} package for Astronomy \citep{astropy13}.
This work additionally relied on Columbia University's \emph{Hotfoot} and \emph{Yeti} compute clusters, and we acknowledge the Columbia HPC support staff for assistance.

>>>>

% packages
\usepackage{amssymb,amsmath,amsbsy}
\usepackage{bbold}
\usepackage{arydshln}
\usepackage{algpseudocode}
\renewcommand\algorithmicthen{}
\renewcommand\algorithmicdo{}
\usepackage{mathrsfs}
\usepackage{subfigure}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{-}

@@

\title{Tidal streams in triaxial systems}
\author{Adrian M. Price-Whelan\altaffilmark{\colum,\adrn},
	    Kathryn V. Johnston\altaffilmark{\colum},
	    Monica Valluri\altaffilmark{\mich},
	    Sarah Pearson\altaffilmark{\colum}}
%	    Andreas H. W. K\"upper\altaffilmark{\colum}}
\date{\centering \today}

@@

\acknowledgements
The authors wish to thank  Andreas K\"upper, Robyn Sanderson, David Hogg, Dan D'Orazio, David Merritt, and the \emph{Stream Team} for useful comments and discussion.
APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155. 
This research made use of Astropy, a community-developed core \texttt{Python} package for Astronomy \citep{astropy13}.
This work additionally relied on Columbia University's \emph{Hotfoot} and \emph{Yeti} compute clusters, and we acknowledge the Columbia HPC support staff for assistance.
